PANCHANGE_data_preprocessing

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
working on the mhd sections for EDGI

```{r glad mhd cleaning}
if(GLAD == TRUE) {
glad.mhd.raw.id <- glad.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd.")
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r edgi mhd copy}
if(EDGI == TRUE) {
  mhd.raw.id <- edgi.mhd.raw.id
}
```

@@

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric = mhd.specific_phobia_e.g._fear_of_flying_numeric,
    mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = mhd.autism_spectrum_disorder_asd_numeric,
    mhd.anorexia_nervosa_unc,
    mhd.atypical_anorexia_nervosa_unc,
    mhd.bulimia_nervosa_unc,
    mhd.psychological_overeating_or_bingeeating_unc
  ) %>%
  add_column(
    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
    mhd.schizoaffective_disorder_numeric = NA
  )
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders. Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
```{r nbr cleaning eating disorders}
if(NBR == TRUE) {
#Recode as 0 if ppt respnds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    mhd.anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.atypical_anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bulimia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
    mhd.psychological_overeating_or_bingeeating_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.psychological_overeating_or_bingeeating_unc_numeric == "0" ~ 0,
                mhd.psychological_overeating_or_bingeeating_unc_numeric == "1" ~ 1)
    )
}

@@

```{r mhd eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

@@

Eating disorders with binge eating vs eating disorders without
Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
```{r mhd restricting_vs_binge_eating_eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 2,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

@@

```{r Check eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.psychological_overeating_or_bingeeating_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating
  )
}
```

>>>>

```{r glad mhd cleaning}
if(GLAD == TRUE) {
glad.mhd.raw.id <- glad.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.bingeeating_disorder = mhd.psychological_overeating_or_bingeeating
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

```{r edgi mhd2 cols}
if(EDGI == TRUE) {
edgi.mhd2.raw <- readRDS(file = paste0(data.raw_path,"/edgi/dem_edgi.rds"))
dim(edgi.mhd2.raw)
colnames(edgi.mhd2.raw)
}
```

```{r edgi mhd2 cleaning}
if(EDGI == TRUE){
  exclude_cols_mhd2 <- c("ID",
                        "Sample",
                        "startDate.prepandemic",
                        "Age_uncleaned",
                        "EduYrs")

  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
    mhd.depression = demographics.depression,
    mhd.pregnancy_depression = demographics.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
    mhd.agoraphobia = demographics.agoraphobia,
    mhd.panic_disorder = demographics.panic_disorder,
    mhd.panic_attacks = demographics.panic_attacks,
    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
    mhd.schizophrenia = demographics.schizophrenia,
    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
#    mhd.personality_disorder_diagnosed = demographics.personality_disorder_diagnosed, # does not exist in EDGI because it is multiple choice in EDGI
    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
    ) %>%
    add_column(
      mhd.schizoaffective_disorder = NA_character_
    ) %>%
    add_numeric(., exclude = exclude_cols_mhd2) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

  # Inspect dimensions
  dim(edgi.mhd2.raw.id)
  # Inspect colnames
  colnames(edgi.mhd2.raw.id)
  #Differences
  dim(edgi.mhd2.raw)[1]-dim(edgi.mhd2.raw.id)[1]
}
```

```{r edgi combine mhd copy}
if(EDGI == TRUE){
mhd.raw.id <- left_join(
  x = edgi.mhd.raw.id,
  y = edgi.mhd2.raw.id,
  by = c("Sample", "ID")
  )

# Inspect dimensions
dim(mhd.raw.id)
# Inspect colnames
colnames(mhd.raw.id)
}
```

@@

nbr.mhd.raw.id <- nbr.mhd.raw %>%
  drop_na(subjectid) %>% # Drop NAs
  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhd."),
    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
    mhd.psychological_overeating_or_bingeeating_unc = mhd.psychological_overeating_or_bingeeating
  ) %>%
  add_column(
    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
    mhd.schizoaffective_disorder_numeric = NA
  )
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders. Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
```{r nbr cleaning eating disorders}
if(NBR == TRUE) {
#Recode as 0 if ppt respnds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    mhd.anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.atypical_anorexia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bulimia_nervosa_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
    mhd.bingeeating_disorder_numeric =
      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_numeric == "0" ~ 0,
                mhd.bingeeating_disorder_numeric == "1" ~ 1)
    )
}

@@

```{r mhd eating_disorders}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.bingeeating_disorder_numeric == "1" ~ 1,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.bingeeating_disorder_numeric == "0") ~ 0
      )
  )

@@

For EDGI does not include other eating disorders, such as purging disorder, rumination disorder, ARFID, or Pica
```{r edgi mhd eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 1, # additional diagnosis in EDGI but not in GLAD
        mhd.bingeeating_disorder_numeric == "1" ~ 1,
        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 1, # additional diagnosis in EDGI
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
          mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
          mhd.atypical_bulimia_nervosa_numeric == "0" &
        mhd.bingeeating_disorder_numeric == "0" &
          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
      )
  )

Eating disorders with binge eating vs eating disorders without
Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
```{r mhd restricting_vs_binge_eating_eating_disorders}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.bingeeating_disorder_numeric == "1" ~ 2,
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
        mhd.bingeeating_disorder_numeric == "0") ~ 0
      )
  )

@@

```{r mhd restricting_vs_binge_eating_eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    restricting_vs_binge_eating_eating_disorders_numeric =
      case_when(
        mhd.anorexia_nervosa_numeric == "1" ~ 1,
        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhd.bulimia_nervosa_numeric == "1" ~ 2,
        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 2, # additional diagnosis in EDGI but not in GLAD
        mhd.bingeeating_disorder_numeric == "1" ~ 2,
        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 2, # additional diagnosis in EDGI
        (mhd.anorexia_nervosa_numeric == "0" &
        mhd.atypical_anorexia_nervosa_numeric == "0" &
          mhd.atypical_anorexia_nervosa_numeric == "0" &
        mhd.bulimia_nervosa_numeric == "0" &
          mhd.atypical_bulimia_nervosa_numeric == "0" &
        mhd.bingeeating_disorder_numeric == "0" &
          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
      )
  )

```{r Check eating_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.bingeeating_disorder
  )
}
```

```{r Check eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder,
  )
}
```
